\textbf{Species and genus plant classification with NEON hyperspectral remote sensing data}

### 2020-10-29 analysis/paper/paper.Rmd
added citations for R and packages

```{r, results='hide', message=FALSE, include=FALSE}
# Extract hyperspectral reflectance data for each individual plant
#R/spectral-lib.Rmd

# Run the main analysis

```

@@

1 - motivation for work, why bother?
  - unprecedented access to unique hyperspectral airborne imagery from NEON (cite)
  - acknowledge additional data to add info (lidar, rgb) (cite) 
  - how meaningful can the HS data alone be to predict species? accuracies? 
  - we expect there to be meaningful information in the HS data for species/genus
2 - knowledge gaps in lit/field?
  - how useful are HS data across many species, ecosystems, geographies? 
  - where is the most important information contained? which wavelengths most important for species discrimination? differ across sites? (cite) 
  - generally more site-specific studies? 
  - prediction of species vs genus? How much easier is genus? Or is this difficult too? (cite hierarchical taxonomic classification recent study)
3 - how we addressed the knowledge gaps
  - the need to generalize methods across locations? --> NEON
  - which wavelengths are most important
  - data harmonization across NEON sites (why are the wavelengths different? Ask NEON person?)

The National Ecological Observatory Network (NEON) is a valuable source of publicly available ecological data across the United States [@keller2008continental].

We have extracted all NEON AOP hyperspectral data for every mapped stem in NEON plots where field data and airborne remote sensing data were collected during the same year.

Here's the code to extract the spectra: [https://gist.github.com/mbjoseph/5c18781e508460e14f64193571b98b7d](https://gist.github.com/mbjoseph/5c18781e508460e14f64193571b98b7d)

@@

Extracted hyperspectral data for all mapped stems at NEON sites
Figure \@ref(fig:fig-spectraExtracted)
Assumed plant locations don't change over time 
Filtered plants to keep only "live" ones
NEON data products (cite)
Spectrometer orthorectified surface directional reflectance mosaic
Woody plant vegetation structure field based measurements
Mask created for water absorption bands (cite)
Packages neonUtilities, geoNEON, neonhs (cite)

@@

```{r fig-studyArea, fig.cap ="Caption", echo=FALSE,  out.width = "450px", message = FALSE, warning=FALSE}
library(here)
knitr::include_graphics(here::here("analysis", "figures", "study_area.pdf"))
```

>>>>

```{r, results='hide', message=FALSE, include=FALSE}
# Extract hyperspectral reflectance data for each individual plant
#R/spectral-lib.Rmd
# Run the main analysis
```

@@

1
* motivation for work, why bother?
* unprecedented access to unique hyperspectral airborne imagery from NEON (cite)
  - acknowledge additional data to add info (lidar, rgb) (cite) 
  - how meaningful can the HS data alone be to predict species? accuracies? 
  - we expect there to be meaningful information in the HS data for species/genus
2 - knowledge gaps in lit/field?
  - how useful are HS data across many species, ecosystems, geographies? 
  - where is the most important information contained? which wavelengths most important for species discrimination? differ across sites? (cite) 
  - generally more site-specific studies? 
  - prediction of species vs genus? How much easier is genus? Or is this difficult too? (cite hierarchical taxonomic classification recent study)
3 - how we addressed the knowledge gaps
  - the need to generalize methods across locations? --> NEON
  - which wavelengths are most important
  - data harmonization across NEON sites (why are the wavelengths different? Ask NEON person?)

The National Ecological Observatory Network (NEON) is a valuable source of publicly available ecological data across the United States [@keller2008continental].
We have extracted all NEON AOP hyperspectral data for every mapped stem in NEON plots where field data and airborne remote sensing data were collected during the same year.

@@

Extracted hyperspectral data for all mapped stems at NEON sites
Figure \@ref(fig:fig-spectraExtracted)
Assumed plant locations don't change over time 
Filtered plants to keep only "live" ones
NEON data products (cite)
Spectrometer orthorectified surface directional reflectance mosaic
Woody plant vegetation structure field based measurements
Mask created for water absorption bands (cite)
We performed our analysis in R [@R] with packages including neonUtilities [@neonUtilities], geoNEON [@geoNEON], neonhs [@neonhs]

The code to do this is provided in the research compendium here:[https://github.com/vscholl/neonHScompendium](https://github.com/vscholl/neonHScompendium).

@@

```{r fig-studyArea, fig.cap ="Study Area", echo=FALSE,  out.width = "450px", message = FALSE, warning=FALSE}
library(here)
knitr::include_graphics(here::here("analysis", "figures", "study_area.pdf"))
```
